### 2025-07-13 conteudo/apendices/gray.tex
update links on apendix to fix mergin issues

Access from \url{https://pmd.github.io/pmd/pmd_userdocs_cpd}.

@@

Access from 
\url{https://cppdepend.com/blog/tracking-the-hidden-duplicate-code-in-a-c-code-base/}.

@@

Access from
\url{https://github.com/dlidstrom/Duplo}.

@@

Access from
\url{https://github.com/duploq/duploq}

@@

Access from
\url{https://simian.quandarypeak.com/}.

@@

Access from
\url{https://codeclimate.com/}.

@@

Access from
\url{https://www.researchgate.net/publication/2866183_Visual_Detection_of_Duplicated_Code}.

@@

Access from
\url{https://github.com/platisd/duplicate-code-detection-tool}

>>>>

Access from \textit{\seqsplit{pmd.github.io/pmd/pmd\_userdocs\_cpd}}.

@@

Access from 
\textit{\seqsplit{cppdepend.com/blog/tracking-the-hidden-duplicate-code-in-a-c-code-base/}}.

@@

Access from
\textit{\seqsplit{github.com/dlidstrom/Duplo}}.

@@

Access from
\textit{\seqsplit{github.com/duploq/duploq}}.

@@

Access from
\textit{\seqsplit{simian.quandarypeak.com/}}.

@@

Access from
\textit{\seqsplit{codeclimate.com/}}.

@@

Access from
\textit{\seqsplit{www.researchgate.net/publication/2866183\_Visual\_Detection\_of\_Duplicated\_Code}}.

@@

Access from
\textit{\seqsplit{github.com/platisd/duplicate-code-detection-tool}}.
